[dcpo_demsupport]

### 2020-06-13 paper/dcpo_demsupport.Rmd
fix years in claassen_input_raw1 to match Claassen's; exclude surveys Claassen omits (this doesn't work perfectly yet pending https://github.com/fsolt/DCPOtools/issues/35)

```{r claassen_input}
claassen_input_raw1 <- read_csv("data/claassen_input_raw.csv") %>% 
  filter(!(str_detect(item, "army") & # WVS obs identified as problematic by Claassen 
    ((country=="Albania" & year==1998) |
         (country=="Indonesia" & (year==2001 | year==2006)) |
         (country=="Iran" & year==2000) |
         (country=="Pakistan" & (year==1997 | year==2001)) | #in DCPO,it is 1997 instead of 1996
         (country=="Vietnam" & year==2001)) |
    (str_detect(item, "strong") &
         ((country=="Egypt" & year==2012) |
              (country=="Iran" & (year==2000 | year==2007)) | #in DCPO, the year is 2007 rather than 2005
              (country=="India") |
              (country=="Pakistan" & (year==1997 | year==2001)) | #in DCPO,it is 1997 instead of 1996
              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
              (country=="Vietnam" & year==2001))))) %>% 
  filter(!(survey=="evs2017" | survey == "arabb5" | survey == "eb471")) %>%  # surveys unused by Claassen
  mutate(item = if_else(item == "strong_amb_1" & year == 2004, "strong_amb_2", item)) # items conflated in amb_combo file

>>>>

```{r claassen_input}
load("data/cys_crosswalk.RData")

claassen_input_raw1 <- read_csv("data/claassen_input_raw.csv", col_types = "cdcddcd") %>% 
  filter(!(str_detect(item, "army_wvs") & # WVS obs identified as problematic by Claassen 
    ((country=="Albania" & year==1998) |
         (country=="Indonesia" & (year==2001 | year==2006)) |
         (country=="Iran" & year==2000) |
         (country=="Pakistan" & (year==1997 | year==2001)) | #in DCPO,it is 1997 instead of 1996
         (country=="Vietnam" & year==2001)) |
    (str_detect(item, "strong_wvs") &
         ((country=="Egypt" & year==2012) |
              (country=="Iran" & (year==2000 | year==2007)) | #in DCPO, the year is 2007 rather than 2005
              (country=="India") |
              (country=="Pakistan" & (year==1997 | year==2001)) | #in DCPO,it is 1997 instead of 1996
              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
              (country=="Vietnam" & year==2001))))) %>% 
  anti_join(cys_to_drop, by = c("country", "year", "survey")) %>% # surveys unused by Claassen
  left_join(cys_crosswalk, by = c("country", "year" = "y_dcpo", "survey")) %>% 
  mutate(year = if_else(!is.na(y_claassen), y_claassen, year)) %>% # use Claassen's year codings
  mutate(item = if_else(item == "strong_amb_1" & year == 2004, "strong_amb_2", item)) # items conflated in amb_combo file
